Frozen Civil Conflicts

### 2024-02-06 paper.qmd
Replace geom_histogram with base hist
ggplot2 is great for everything except histograms.

[//]: # Setup R environment
```{r setup, include = F}
library(dplyr)
library(ggplot2)
library(ggthemes)
library(ggdist)
library(knitr)
library(patchwork)
library(tidyr)

@@

```{R}
sbc <- readRDS("./posteriors/sbc.rds") |>
    select(-.chain, -.iteration, -.draw) |>
    pivot_longer(everything())

ggplot(sbc, aes(x = value)) +
    geom_histogram(bins = 10) +
    facet_wrap(~ name, scales = "free") +
    theme(axis.title.y = element_blank(),
          axis.title.x = element_blank())
```

@@

```{R}
pzero <- function(x) mean(x > 0)

models <- list.dirs("posteriors", recursive = F)
stopifnot(length(models) != 0)

>>>>

[//]: # Setup R environment
```{r setup, include = F}
library(dplyr)
library(ggplot2)
library(ggthemes)
library(ggdist)
library(latex2exp)
library(knitr)
library(patchwork)
library(tidyr)

@@

```{R}
sbc <- readRDS("./posteriors/sbc.rds") |>
    select(-.chain, -.iteration, -.draw)

# I really, really hate ggplot histograms
par(family = "TeX Gyre Pagella", mfrow = c(5, 5),
    mai = c(0.35, 0.2, 0.1, 0.2), mgp = c(1.75, 0.5, 0))
for (i in seq_along(sbc)) {
    # I also hate tibbles with every fiber of my being
    label <- colnames(sbc)[i] |> stanvar_latex()
    sbc[[i]] |> hist(main = "", xlab = TeX(label), ylab = "")
}
```

@@

```{R}
models <- list.dirs("posteriors", recursive = F)
stopifnot(length(models) != 0)
